\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.5in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}
\usepackage{multicol}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

\begin{document}

\begin{center}
    {\Huge \textbf{HAMID RAFIQUE}} \\
    \vspace{4pt}
    Lahore, Pakistan | +92 324-6763616 \\
    \href{mailto:hamidch0866@gmail.com}{hamidch0866@gmail.com} | \href{https://github.com/ihamidch}{GitHub} | \href{https://linkedin.com/in/hamid-rafique-a75b9a3a5}{LinkedIn}
\end{center}

\section{Education}
\textbf{University of Sahiwal (UoS)} \hfill Sahiwal, Pakistan \\
\textbf{Bachelor of Science in Computer Science} \hfill 2021 -- 2025 \\
Cumulative GPA: 3.47 / 4.0

\section{Experience}

\textbf{INTRAGUARD} \hfill Remote, UK Based \\
\textit{Software Developer} \hfill Sep 2025 -- Present \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item Developed and maintained full-stack MERN web applications with a focus on scalability.
    \item Contributed to an industry-level product with GraphQL API integration.
\end{itemize}

\vspace{6pt}

\textbf{METALOGICS} \hfill Lahore, Pakistan \\
\textit{React.js Developer (MERN Stack)} \hfill 2024 -- 2025 \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item Developed responsive user interfaces using React.js and integrated them with Node.js backends.
    \item Managed state using Redux/Context API and optimized MongoDB queries for performance.
\end{itemize}

\vspace{6pt}

\textbf{FLUXXION} \hfill Remote, Pakistan \\
\textit{Data Analysis Intern} \hfill May 2025 -- Jul 2025 \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item Conducted data cleaning, transformation, and visualization using Power BI and Python.
    \item Developed SQL queries for extracting key business metrics and patterns.
\end{itemize}

\vspace{6pt}

\textbf{CYBERWINGS.PK} \hfill Lahore, Pakistan \\
\textit{DevOps Engineer Associate} \hfill 2025 \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item Automated infrastructure for Python and Node.js applications using Terraform and AWS.
    \item Containerized complex AI workflows using Docker for high availability.
\end{itemize}

\section{Technical Skills}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item \textbf{Programming Languages:} Python, JavaScript, C++, SQL (MS-SQL, MySQL), HTML5, CSS, LaTeX
    \item \textbf{Frameworks \& Libraries:} MERN stack, Next.js, FastAPI, LangChain, TailwindCSS, GraphQL
    \item \textbf{Tools \& Platforms:} Git, GitHub, Docker, AWS, Terraform, VS Code, Postman, Power BI
\end{itemize}

\section{Selected projects (aligned with portfolio)}

\textbf{Production MERN — live on Vercel (each app: own frontend + API; showcased on personal portfolio)} \hfill 2024 -- 2025

\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item \textbf{\href{https://ecommerece-mern-web.vercel.app/}{E-commerce Platform}} — MERN, Express, MongoDB. \href{https://github.com/ihamidch/Ecommerece}{Repository.}
    \item \textbf{\href{https://frontend-kappa-amber-29.vercel.app/}{Freelancer Marketplace}} — MERN, jobs and applications. \href{https://github.com/ihamidch/Freelancer-Marketplace}{Repository.}
    \item \textbf{\href{https://talentscout-ai-web.vercel.app/}{TalentScout AI}} — MERN, resume screening, optional Llama/Groq via \texttt{AI\_ENGINE\_URL}. \href{https://github.com/ihamidch/talentscout-ai}{Repository.}
    \item \textbf{\href{https://porfolio-alpha-murex.vercel.app/}{Developer portfolio}} — Next.js 15, Framer Motion; highlights MERN deployments and DevOps. \href{https://github.com/ihamidch/porfolio-}{Repository.}
\end{itemize}

\vspace{6pt}

\textbf{Additional projects} \hfill \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item \textbf{\href{https://aqua-insights.vercel.app/}{Aqua Insights}} — Python, ML, water-quality assessment.
    \item \textbf{\href{https://drive.google.com/file/d/1YGeR2VAcuSMpikYF-UIMuGQRbnowNqrJ/view}{MoodSnap}} — Flutter, Python, AI, image processing.
    \item \textbf{\href{https://sehat-online-frontend.vercel.app/}{Sehat Online}} — Next.js, MSSQL, NLP chatbot.
\end{itemize}

\newpage

\section{Leadership and Extracurricular}

\textbf{Dr. Coders Ambassador} \hfill July 2025 -- Sep 2025 \\
\textit{Dr. Coders, Pakistan} \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item Led student engagement initiatives, coordinated coding activities, and represented Dr. Coders.
\end{itemize}

\vspace{6pt}

\textbf{MT bytes Ambassador} \hfill July 2025 -- Oct 2025 \\
\textit{MT. bytes, Pakistan} \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item Demonstrated leadership by organizing peer learning sessions and tech programs.
\end{itemize}

\vspace{6pt}

\textbf{Microsoft Learn Student Ambassadors (MLSA)} \hfill Oct 2023 -- Dec 2025 \\
\textit{Beta MLSA} \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item Serving as a Beta MLSA, conducting workshops and technical sessions for student engagement.
\end{itemize}

\vspace{6pt}

\textbf{Microsoft Learn SA -- University of Sahiwal Chapter} \hfill Sep 2024 -- Dec 2025 \\
\textit{Co Director Team Management} \\
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item Leading the management team of the UoS MLSA chapter, coordinating events, and mentoring peers.
\end{itemize}

\section{Certifications and Courses}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=0.15in]
    \item \textbf{HCIA -- Huawei AI Certification | Huawei:} Covered fundamentals of AI and machine learning.
    \item \textbf{Azure Data Scientist Associate | Microsoft:} Model training and deployment.
    \item \textbf{Data Mining and Business Intelligence | NAVTTC (University of Sahiwal).}
    \item \textbf{Fundamentals of Agile Project Management | PMI:} Gained understanding of Scrum delivery.
    \item \textbf{Problem Solving \& SQL | HackerRank:} Strengthened algorithmic thinking and SQL manipulation.
\end{itemize}

\end{document}
